Training a Gaming Agent on Brainwaves

### 2020-07-07 review/response.letter.tex

P4 referring to Fig 6; a comparison ROC curve with subject 1 would be more interesting

\begin{quotation}
{\color{blue}
We added the ROC Curve for subject 1.
}
\end{quotation}

P5, 34 what is meant by “experiences”?

\begin{quotation}
{\color{blue}
HAY QUE REVISAR BIEN QUE QUEREMOS DECIR CON ESTO.
}
\end{quotation}

\begin{quotation}
{\color{blue}
ESTO LO PODEMOS HACER ES ELIMINAR ESO DEL GRAFICO
}
\end{quotation}

\begin{quotation}
{\color{blue}
EN ESTA LA IDEA SERIA RESPONDER QUE ES POSIBLE HACERLO PORQUE EL AGENTE SI NO LO ENTRENAS NO MEJORA Y SI LO ENTRENAS AUN CON DATOS POBRES SI MEJORA.
}
\end{quotation}

\begin{quotation}
{\color{blue}
TIENEN USTEDES EL CODIGO PARA GENERAR ESTAS FIGURAS?  SERIA PARA AGRANDAR EL TEXTO
}
\end{quotation}

Page 6, 40
“However, even though this implies that the agent misses frequently that an action taken is wrong, this is not hindering the overall performance and the agent is still learning.”
// Your results show that this is subject dependent

@@

\begin{quotation}
{\color{blue}
TIENEN USTEDES EL CODIGO PARA GENERAR ESTAS FIGURAS?  SERIA PARA AGRANDAR EL TEXTO
}
\end{quotation}

Page 6, 40
“However, even though this implies that the agent misses frequently that an action taken is wrong, this is not hindering the overall performance and the agent is still learning.”
// Your results show that this is subject dependent

\begin{quotation}
{\color{blue}
This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
}
\end{quotation}

P6, 56
Results show that training a classifier with data of one subject, but using it
to classify the events of experiences of another subject does
not lead to an improvement on the performance of the agent.

\begin{quotation}
{\color{blue}
ACA NO ESTOY SEGURO QUE QUISO DECIR
}
\end{quotation}

@@

\vskip+1ex
\noindent \dotfill
\vskip+1ex

\subsection*{\ovalbox{Reviewer 3 General Comments}}

Comments to the Author
The following work shows the usage of ErrPs for training a gaming agent using reinforcement learning. Authors attempt different conventional classification approaches, as well as intersubject classification.

\begin{quotation}
{\color{blue}
We appreciate a lot the time dedicated to review our manuscript.
}
\end{quotation}

@@

It is unclear to me the benefit of evaluating single subject to single subject offline classification accuracy. Please elaborate on this.

\begin{quotation}
{\color{blue}
ErrP detection and experimentation is not an straightforward.  We tested many variants of the game and none could produce the ErrP.  We aimed to have a simple solution, a simple game.  The single subject accuracy that we show on Figure 6 are illustrative that the level of ErrP single trial identification that we achieved for different subjects (which is low).  We wanted to emphasize the finding that even with such low levels of identification (which is a common issue in BCI research \cite{REF}, it was possible for the agent to learn an efficient strategy.
}
\end{quotation}

@@

Since different subjects attained different performance, all combinations of subjects used for training and testing should be inspected for the 1:1 evaluation setup.

\begin{quotation}
{\color{blue}
ESTE SERIA UN GRAFICO EN UNA TABLA DE 8X8 DONDE SE MUESTRAN TODAS LAS COMBINACIONES POSIBLES. CREEN QUE ESTO SERIA ALGO FACTIBLE ?
}
\end{quotation}

@@

Maybe classification accuracy could be reported at different steps (depending on the amount of training data – gradual increasing the number of subjects)

\begin{quotation}
{\color{blue}
CREO QUE APUNTA A ARMAR ALGUN GRAFICO QUE MUESTRE COMO VA MEJORANDO LA CLASIFICACION A MEDIDA QUE SE VA VARIANDO LOS CONJUNTOS DE TRAINING/TESTING.  NO TIENEN ALGO ASI NO ?
}
\end{quotation}

@@

What is the ratio of hit/no hit segments of action (epochs)?

\begin{quotation}
{\color{blue}
PARA CADA EXPERIENCIA, SE ACUERDAN CUAL ES LA RELACION HIT (TIENE ERRP)/NO HIT DE TODOS LOS MOVIMIENTOS QUE SE HACEN EN UNA SOLA CORRIDA ?
}
\end{quotation}

@@

Page 3, column 2, lines 4-9. It is unclear at this stage what action from the starting point would generate an ErrP.
moves-> move

\begin{quotation}
{\color{blue}
MMMMMMM
}
\end{quotation}

Page 3, column 2, lines 11-13. Has the MinMax Scaler been applied in any other BCI related study or elsewhere? I think including a reference would be useful.

\begin{quotation}
{\color{blue}
AGREGAR REFERENCIAS DE ALGUN OTRO ESTUDIO QUE USE MINMAX SCALER PARA BCI
}
\end{quotation}

@@

Page 4. Figure 3. I would suggest adding another set of bars for the grand average classification scores.

\begin{quotation}
{\color{blue}
LO QUE PIDE ACA EL REVISOR ES AGREGAR UNA BARRA MAS A CADA SUJETO CON LA CLASIFICACION HACIENDO PROMEDIO DE TODAS LAS SENALES.  MMMM Cre que esto sería dificil tenerlo....
}
\end{quotation}

@@

Page 4, Figure 4. This figure is redundant and could be removed.

\begin{quotation}
{\color{blue}
YO CREO QUE SERIA MEJOR REEMPLAZAR LA FIGURA 3 CON UNA FIGURA QUE MUESTRE LO MISMO PERO MAS CLARA.  TIENEN USTEDES ALGUNA FIGURA ASI ?
}
\end{quotation}

@@

Page 5, Figure 5. The titles of the subplots would be more descriptive when replacing the letters with the corresponding subjects number.

\begin{quotation}
{\color{blue}
We agree with Reviewer's comment.  We removed the letters and replace them with subject's numbers.
}
\end{quotation}

@@

Page 5, column1, line 55, accumulative->cumulative

\begin{quotation}
{\color{blue}
Fixed.
}
\end{quotation}

Page 6, Figure 8. It is unclear to me what is the benefit of showing both A and B. Since the behavior is similar in both cases.

\begin{quotation}
{\color{blue}
TIENE RAZON.  ACA PODEMOS MOSTRAR TODAS LAS CURVAS RESUMIDAS.  EL TEMA ES QUE HAY QUE CAMBIAR LOS LABELS PARA QUE PUEDAN AJUSTARSE COMO SI FUESEN GRAFICOS CHICOS, QUEDARIA DE 4X4.
}
\end{quotation}

@@

Page 6, Figure 10. This figure is, in my opinion, incomplete. What is the reason for showing this subset of subjects? I suggest showing the confusion matrices of all subjects and/or their average.

\begin{quotation}
{\color{blue}
HAY QUE MOSTRAR TODAS LAS MATRICES DE CONFUSION.
}
\end{quotation}

### 2020-07-07 ErrP.tex
Primera iteración de la carta de respuesta.

Electroencephalographic signals have high inter-subject variability~\cite{Chavarriaga2014}.   This is evidenced in Figure~\ref{fig:transferlearning} where the agent training is performed by using rewards obtained by classifying epochs from one subject, but using a classifier which was trained using the brainwaves from a different subject.   Not performance gain is evidenced, the agents learn nothing which implies that the reward information is useless.

@@

Finally, Figure~\ref{fig:avg_steps_all} shows the result of training an agent with accumulative experiences from subjects 1,2,3,4,7, and 8.  It can be seen that the overall performance of the agent improves as long as there are more experiences to be used to train it, regardless if they were generated from the brainwaves classification from different subjects.

@@

Concluding, this research show evidence that brain signals can be used as an interface between human and a gaming computer enabling an alternative communication with the system without explicit input from the user.

>>>>

Electroencephalographic signals have high inter-subject variability~\cite{Chavarriaga2014}.   This is evidenced in Figure~\ref{fig:transferlearning} where the agent training is performed by using rewards obtained by classifying epochs from one subject, but using a classifier which was trained using the brainwaves from a different subject.   No performance gain is evidenced, the agents learn nothing which implies that the reward information is useless.

@@

Finally, Figure~\ref{fig:avg_steps_all} shows the result of training an agent with cumulative experiences from subjects 1,2,3,4,7, and 8.  It can be seen that the overall performance of the agent improves as long as there are more experiences to be used to train it, regardless if they were generated from the brainwaves classification from different subjects.

@@

Concluding, this research shows evidence that brain signals can be used as an interface between human and a gaming computer enabling an alternative communication with the system without explicit input from the user.
